Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-10 pkg/disttree/inst/draft/draft.Rnw
move all new comments about Easty Tyrol to Section 3.4, some streamlining
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2459 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 222b3af3a649bb2f808931a750f1359e9e91411d

@
\caption{\label{fig:all-map}Map of Tyrol coding the best-performing model
for each station (type of symbol) when learned on 1985--2008 and validated for 2009--2012.
The color codes whether the distributional 
forest had higher (green) or lower (red) CRPS compared to the best of the 
other three models. The background shows the local topography \citep{Robinson:2014}.
Station Axams is highlighted in bold.}
\end{figure}

@@

To assess whether these differences in predictive performance are due to differences
in the topography, Figure~\ref{fig:all-map} shows a brief spatial summary of all
stations. Each station is illustrated by a symbol that conveys which
model performed best in terms of CRPS on the last 4~years of the data.
Additionally, the color of the symbol indicates the CRPS difference between 
distributional forest and the best-performing other model. Green signals that
the distributional forest performs better than the other models whereas red
signals that another model performs better. Overall the distributional forest
performs on par (gray) or better (green) for the majority of stations. Only
for a few stations in the north-east EMOS performs best, and in East Tyrol
the prespecified GAMLSS performs particularly well in the validation period
(2009--2012).

@@

The supplement shows that some of the differences in forecast skill from
Figure~\ref{fig:all-map} even out in the cross-validation with distributional
forests typically performing at least as well as the best of the other models at most
stations. In particular, this also includes three stations in East Tyrol
where the prespecified GAMLSS performs best in the single-split setting
(learning based on 1985--2008 and validation for 2009--2012). While part of
the performance difference can also be attributed to different
climatological characteristics in East Tyrol (that, unlike North Tyrol, is located
south of the main Alpine Ridge), the differences are greatly reduced for several
stations in East Tyrol by considering more splits in the full cross-validation.

>>>>

@
\caption{\label{fig:all-map}Map of Tyrol coding the best-performing model
for each station (type of symbol) when learned on 1985--2008 and validated for 2009--2012.
The color codes whether the distributional 
forest had higher (green) or lower (red) CRPS compared to the best of the 
other three models. The gray background shows the local topography \citep{Robinson:2014}.
Station Axams is highlighted in bold.}
\end{figure}

@@

To assess whether these differences in predictive performance are due to differences
in the topography, Figure~\ref{fig:all-map} shows a brief spatial summary of all
stations. Each station is illustrated by a symbol that conveys which
model performed best in terms of CRPS on the last 4~years of the data.
Additionally, the color of the symbol indicates the CRPS difference between 
distributional forest and the best-performing other model. Green signals that
the distributional forest performs better than the other models whereas red
signals that another model performs better. Overall the distributional forest
performs on par (gray) or better (green) for the majority of stations. Only
for a few stations in the north-east EMOS performs best, and in East Tyrol
the prespecified GAMLSS performs particularly well in the validation period
(2009--2012). \hlc{Partially, this can be attributed to random variation as
the differences at several stations are mitigated when considering a full
cross-validation rather than a single split into learning and validation period}
\citep[see Supplement~A,][and the corresponding discussion in the next section]{Schlosser+Hothorn+Stauffer:2018a}.
\hlc{Further differences are possibly due to East Tyrol lying in a different
climate zone, south of the main Alpine Ridge. Hence, long-term climatological
characteristics as well as the precipitation patterns in 2009--2012 differ
from North Tyrol, conforming particularly well with the additive effects from
the prespecified GAMLSS.}

@@

The supplement shows that some of the differences in forecast skill from
Figure~\ref{fig:all-map} even out in the cross-validation with distributional
forests typically performing at least as well as the best of the other models at most
stations. In particular, this also includes three stations in East Tyrol
where the prespecified GAMLSS performs best in the single-split setting
(learning based on 1985--2008 and validation for 2009--2012).
